Predictive Regressions with Persistent Regressors:\\ Monte Carlo evidence for the Bonferroni Q-test

### 2019-09-18 paper.tex
ADD Bollerslev (1986)

It is therefore interesting to observe the behavior of the Bonferroni Q-test if innovations are modeled by a generalized autoregressive conditional heteroskedasticity [GARCH] process that approaches covariance nonstationarity. If the regressor is a valuation ratio, it seems sensible that there is a more or less stable correlation between the regressor and stock returns. A multivariate GARCH model that allows such a restriction is the Constant Conditional Correlations GARCH  [CCC-GARCH] model of \citet{bollerslev1990modelling}. It is defined as follows. Let $ \boldsymbol{z_{t}}$ be a bivariate standard normal random variable, i.e., $ \boldsymbol{z}_{t} \stackrel{i i d}{\sim} \mathrm{N}\left(\mathbf{0}, \boldsymbol{I}_{2}\right)$. Then the innovations are modeled as 

@@

in $\boldsymbol{D}_{t}$ are modeled by independent univariate GARCH processes, i.e.,

>>>>

It is therefore interesting to observe the behavior of the Bonferroni Q-test if innovations are modeled by a generalized autoregressive conditional heteroskedasticity [GARCH] process of \citet{bollerslev1986generalized} that approaches covariance nonstationarity. If the regressor is a valuation ratio, it seems sensible that there is a more or less stable correlation between the regressor and stock returns. A multivariate GARCH model that allows such a restriction is the Constant Conditional Correlations GARCH  [CCC-GARCH] model of \citet{bollerslev1990modelling}. It is defined as follows. Let $ \boldsymbol{z_{t}}$ be a bivariate standard normal random variable, i.e., $ \boldsymbol{z}_{t} \stackrel{i i d}{\sim} \mathrm{N}\left(\mathbf{0}, \boldsymbol{I}_{2}\right)$. Then the innovations are modeled as 

@@

in $\boldsymbol{D}_{t}$ are modeled by independent univariate GARCH processes according to \citet{bollerslev1986generalized}, i.e.,
